Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-20 papers/paper-eccentricity/paper-eccentricity.tex
First version of Intro done, minor additions

The complex nature of SMBH coalescence in a galaxy merger setting necessitates the use of numerical techniques \citep[e.g.][]{Berentzen2009,Khan2011,Mannerkoski2019}
to provide quantitative predictions for observational programmes such as ground-based pulsar timing arrays \citep[PTAs, e.g.][]{Lentati2015,Verbiest2016,Arzoumanian2020} and the upcoming Laser Interferometer Space Antenna \citep[LISA, e.g.][]{Amaro-Seoane2023} space mission.
Understanding how faithfully SMBH binary eccentricity is captured in numerical simulations is thus a critical piece of the puzzle in constraining the SMBH merger rate
that the observational GW community aims to detect.

>>>>

The complex nature of SMBH coalescence in a galaxy merger setting necessitates the use of numerical techniques \citep[e.g.][]{Berentzen2009,Khan2011,Dosopoulou2017,Mannerkoski2019}
to provide quantitative predictions for observational programmes such as ground-based pulsar timing arrays \citep[PTAs, e.g.][]{Lentati2015,Verbiest2016,Arzoumanian2020} and the upcoming Laser Interferometer Space Antenna \citep[LISA, e.g.][]{Amaro-Seoane2023} space mission.
Understanding how faithfully SMBH binary eccentricity is captured in numerical simulations is thus a critical piece of the puzzle in constraining the SMBH merger rate
that the observational GW community aims to detect.
